Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-16 preliminaries.tex

@@

\begin{definition}
	Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ (and $1^{1/\eps}$ for the case of $\SampBQP$ problem), and verifier's private input $x\in\zo^*$.
	We say $\Pi$ is \emph{blind} if for all cheating $\BQP$ prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
	\begin{itemize}
		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda, 1^{1/\eps})}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda, 1^{1/\eps})}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
	\end{itemize}
\end{definition}

>>>>

\begin{remark} Note that we do not parameterize the soundness error in Definition \ref{dfn:stats-secure-proto-sampbqp}. This is because the definition of $\SampBQP$ already includes an error parameter $\eps$, where the algorithm is allowed to generate a sample with statistical error up to $\eps$ in time polynomial in $1/\eps$. Hence, in our definition of soundness, we allow the verifier's output to have error $\eps$ for any given inverse polynomial $\eps$. 
\end{remark}

@@

\begin{definition}[Blindness]
	Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ (and $1^{1/\eps}$ for the case of $\SampBQP$ problem), and verifier's private input $x\in\zo^*$.
	We say $\Pi$ is \emph{blind} if for all cheating $\BQP$ prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
	\begin{itemize}
		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda, 1^{1/\eps})}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda, 1^{1/\eps})}_{\lambda\in\bbN, \eps\in(0,1), x\in\zo^*}$
	\end{itemize}
\end{definition}
